# Decision Tree and Random Forest

### Problem Statement:- 

    - A cloth manufacturing company is interested to know about the segment or attributes contributing to high sale.

### Data Understanding

```{r}
library(readr)
cd <- read_csv("/Users/thanush/Desktop/Digi 360/Module 19/Company_Data.csv")
head(cd)
```

```{r}
# Renaming the columns
colnames(cd) <- c("sales","comp_price","inc","adv","pop", "price", "sloc", "age","edu","urban","us")
head(cd)
```

```{r}
# converting outpout variable to categorical
cd$sales <- ifelse(cd$sales > 8,"Yes","No")
head(cd)
```


```{r}
#converting features into factor
cd$sloc <- as.factor(cd$sloc)
cd$urban <- as.factor(cd$urban)
cd$us <- as.factor(cd$us)
cd$sales <- as.factor(cd$sales)
```

```{r}
str(cd)
```


### Splitting the dataset into test and train

```{r}
sales_high <- cd[cd$sales == "Yes",] 
sales_low <- cd[cd$sales == "No",]

```


```{r}
train <- rbind(sales_high[1:131,], sales_low[1:189,])
test <- rbind(sales_high[132:164,], sales_low[190:236,])
```

### Building the model

```{r}
# Loading the rpart library for building the model
library(rpart)
library(rpart.plot)
```

```{r}
# Let's build the model on train data
model_tree <- rpart(sales~., data=train, method = 'class', cp=.02)
```

### Plotting a Tree

```{r}
# Plotting the Tree Graph
rpart.plot(model_tree,box.palette="RdBu", shadow.col="gray", nn=TRUE)
```

### Predictions on Train Data

```{r}
# Accuracy of training data
train_pred = predict(model_tree,train,type="class")
confMat <- table(train$sales,train_pred)
```

### Train Data Accuracy

```{r}
accuracy <- sum(diag(confMat))/sum(confMat)
accuracy
```

### Predictions on test data

```{r}
test_pred = predict(model_tree,test,type="class")
confMat <- table(test$sales,test_pred)
```

### Test data accuracy

```{r}
accuracy <- sum(diag(confMat))/sum(confMat)
accuracy
```

### Cross Table

```{r}
library(gmodels)
CrossTable(test$sales, test_pred)
```

### Conclusion

    - There is not much deviation in the accuracy between train and test data
    - Accuracy of test data is 73%
    
We conclude that our model has classified the sales with accuracy of 73%. 
