# Decision Tree and Random Forest

### Problem Statement:- 

    - Divide the data (Diabetes) into training and test datasets and create a Random Forest Model to classify 'Class Variable'.

### Data Understanding

```{r}
library(readr)
db <- read_csv("/Users/thanush/Desktop/Digi 360/Module 19/Diabetes.csv")
head(db)
```

```{r}
# Renaming the columns
colnames(db) <- c("np","plasma","dbp","tsf_thick", "serum", "BMI", "pedigree", "age", "class")
head(db)
```

```{r}
table(db$class)
```


```{r}
#converting features into factor
db$class <- as.factor(db$class)
```

```{r}
str(db)
```

```{r}
# Checking for missing values
sapply(db, function(x) sum(is.na(x)))
```


### Splitting the dataset into test and train

```{r}
# Taking only the same number of data points from majority class.
library(caret)
set.seed(1000)
index <- createDataPartition(y = db$class, p = 0.7, list = FALSE)
train <- db[index, ]
test <- db[-index, ]
```

```{r}
head(train)
```

### Building the model

```{r}
# Loading the randomForest library for building the model
library(randomForest)
```

```{r}
# Let's build the model on train data
model_tree <- randomForest(class~., data=train, mtry = 8, ntree=500, importance=TRUE)
```

### Plotting a Tree

```{r}
# Plotting the Tree Graph
plot(model_tree)
```

### Predictions on Train Data

```{r}
train_pred <- predict(model_tree, newdata = train)
```

### Confusion Matrix

```{r}
confMat = table(train$class, train_pred)
confMat
```

### Train Data Accuracy

```{r}
train_acc <- sum(diag(confMat))/sum(confMat)
train_acc
```


### Predictions on Test data

```{r}
test_pred <- predict(model_tree, newdata = test)
```

### Confusion Matrix 

```{r}
confMat = table(test$class, test_pred)
confMat
```

### Test data accuracy

```{r}
test_acc <- sum(diag(confMat))/sum(confMat)
test_acc
```

### Conclusion

    - There is significant deviation in the accuracy between train and test data
    - Accuracy of test data is 77%
    
We conclude that our model has done `diabetes` classification with accuracy of 77%. 
